Timeliness of security updates for Android

### 2014-10-28 securityupdates.tex
Show non security updates on the security updates graph for comparison

The number of devices getting security updates each week, is shown in Figure~\ref{fig:weekly_security_updates}, blue shows updates which changed the Android version number from a version with known vulnerabilities to one which had fewer known vulnerabilities.
Red indicates updates which changed the build number but not the version number and so might contain a backported fix for a vulnerability.

>>>>

The number of devices getting security updates each week, is shown in Figure~\ref{fig:weekly_security_updates}, blue shows updates which changed the Android version number from a version with known vulnerabilities to one which had fewer known vulnerabilities.
Green indicates updates which changed the build number but not the version number and so might contain a backported fix for a vulnerability.
Red indicates updates which did not fix security vulnerabilities (because there were know known security vulnerabilities in the version of Android they were already running).
